Initial Analysis

### 2019-09-16 Initial_Analysis.Rmd
Continued to eddit circular plot. Set new list of spp to Gabriel (~800). Fixed error in EstTranSpp fun

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "wesanderson",
  "circlize", # For circular plot
  "EBImage", #for reading images to the circular plot
  # "cowplot",
  # "rgdal",
  # "RColorBrewer",
  # "knitr",
  # "kableExtra",
  "ggrepel", # for nice plot labels
  "ggsflabel", # for nice sf_plots labels
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "stringr",
  # "stringer",
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
  "parallel", # for parallelization
  "taxize", # For getting species names
  "rfishbase" # for species ecosystem affinity
)

@@

@@

#### List of species we have data for...

# Removes everything before the number
Step_One <- gsub(".*_","",list.files("/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Distribution_Data/SAU_Distribution/"))

# Get All SAU species for the final analysis

@@

#### EEZ

@@

#### For testing 
# Spp <- 604250  # Anchovie Equator, Chile and Peru
# Spp <- 600107 # Tuna Many RFMOs
# Spp <- 600464 # Discrete species 
# x <- c(600464, # Discreat spp in one nation
      # 600059, # nowhere to be found spp
       # 601352, # Discrete spp in two nations
       # 600004) # transboundary spp
# Model <- "All"
# Coord <- CoorG
# 
# # For EEZ
# Neighbours <- Neighbours_Data
# Index_Code <- Index_Code
#  
# __________________________________
# __________________________________

# The function
EstTransIndex <- function(Spp,Model,Neighbours,Coord,Index_Code,Save="Y",Jurisdiction_Type){

@@

  if(nrow(Spp_Grid) == 0 & Save == "Y"){

    # IF SPECIES IS DISCRETE AND ONLY APEARS IN ONE REGION
  Discrete_Territory <- unique(Model_Index_D$Territory)
  n_Territory <- length(Discrete_Territory)

@@

    # Get current Spp that is not transboundary 
    Current_Spp <- tibble(TaxonKey = as.integer(Spp),
                          Territory = Discrete_Territory)

@@

    if(n_Territory ==1){

    To_Print <- paste(Spp, "is only present in",Discrete_Territory)
    print(To_Print)
    paste(Spp, "is only present in",Discrete_Territory)
    }else{

      To_Print <- paste(Spp, "is in both (non-neighbouring)",Discrete_Territory[1],Discrete_Territory[2])
      print(To_Print)
    }

@@

  if(nrow(Spp_Grid) > 0 & Save == "Y"){

@@

  # Merge dataframes to get totals per Neighbourds
  Area_Index_D <- full_join(Territory_T,
                            Neighbour_T, 
                            by = c("Model_Index","Name","TaxonKey")
  ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(Neighbour = Name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbour = n_spp_eez.y) %>% 
    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
    select(1:3,6,8)

  #____________ FINAL INDEX TABLE_________ #
  Indexes <- Model_Index_D %>% 
    # rename(Territory = Name) %>% 
    full_join(Area_Index_D,
              by = c("TaxonKey","Territory","Model_Index")
    ) %>% 
    filter(!is.na(Area_Index),
           !is.na(Model_Index) # Uncomment after producing Models x datasets
    ) %>%  # Remove cases where the country does not pass the area_index and viceversa
    select(TaxonKey,Territory,Neighbour,everything())

@@

  } # Closes Treshold 3
}

@@

@@

# Load Jursidiction-dependant data
if(Jurisdiction == "EEZ"){
  # Load neighbours data from previouse routine
  Neighbours_Data <- fread(paste(Data_Path,"Spatial_Data/EEZ_Neighbours_List.csv", sep =""))

@@

  # Load neighbours data from previouse routine
  Neighbours_Data <- fread(paste(Data_Path,"Spatial_Data/RFMO/RFMO_Neighbours_List.csv", sep =""))

  Index_Code <- fread(paste(Data_Path,"Spatial_Data/RFMO/RFMO_Index_Code.csv", sep =""))

@@

# Just a warning for me not to forget
print(paste("You are running the model for",nrow(Exploited_Species),"Species at the",Jurisdiction,"level"))
```

@@

@@

# In case you want to use old results (ran with older verion of neighbours)
# Results_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Old_Results/"

@@

  # List of species
  Spp <- list.files(paste(Results_Path,"/Trans_Results",sep=""))[1:672]

  # ---------------------------- #
  # Load and clean Transboundary results
  Results_Trans <- GetTransResults(Spp)

  # Clean out countries that share with their own borders (e.g. USA gulf of Mx and East coast)
  Auto_Remove_Territories <- Results_Trans %>%   
    rename(FishingRegion=Territory) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(TaxonKey,
           Territory= FishingRegion,
           FishingRegion=Neighbour, #Neighbour_Territory
           Model_Index,
           Area_Index,
           CT_fishing_entity= fishing_entity) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(1,2, 
           Neighbour = FishingRegion,
           Model_Index:CT_fishing_entity,
           NT_fishing_entity= fishing_entity,
           everything()) %>% 
    mutate(
      CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Territory),paste(CT_fishing_entity)),
      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour),paste(NT_fishing_entity)),
      Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
    )

  Territories_to_Remove <- Results_Trans %>% 
    filter(
      Territory %in% Islands_to_Remove |
        Neighbour %in% Islands_to_Remove |
        Territory == "Balearic Island (Spain)" & Neighbour == "Spain (Mediterranean and Gulf of Cadiz)" |
        Territory == "British Virgin Isl. (UK)" & Neighbour == "Anguilla" |
        Neighbour == "British Virgin Isl. (UK)" & Territory == "Anguilla" |
        Territory == "Corsica (France)" & Neighbour == "France (Mediterranean)" |
        Neighbour == "Corsica (France)" & Territory == "France (Mediterranean)" |
        Territory == "Crete (Greece)" & Neighbour == "Grece" |
        Neighbour == "Crete (Greece)" & Territory == "Grece" |
        Territory == "Cyprus (North)" & Neighbour == "Cyprus (South)" |
        Neighbour == "Cyprus (North)" & Territory == "Cyprus (South)" |
        Territory == "Channel Isl. (UK)" & Neighbour == "United Kingdom" |
        Neighbour == "Channel Isl. (UK)" & Territory == "United Kingdom" |
        Territory == "Glorieuse Islands (France)" & Neighbour == "Mayotte (France)" |
        Neighbour == "Glorieuse Islands (France)" & Territory == "Mayotte (France)" |
        Territory == "Guam (USA)" & Neighbour == "Northern Marianas (USA)" |
        Neighbour == "Guam (USA)" & Territory == "Northern Marianas (USA)" |
        Territory == "Italy" & Neighbour == "Sardinia (Italy)" |
        Neighbour == "Italy" & Territory == "Sardinia (Italy)" |
        Territory == "Italy" & Neighbour == "Sicily (Italy)" |
        Neighbour == "Italy" & Territory == "Sicily (Italy)" |
        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (main islands)"|
        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (main islands)"|
        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (Ogasawara Islands)"|
        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (Ogasawara Islands)"|
        Territory == "Norway" & Neighbour == "Svalbard Isl. (Norway)" |
        Neighbour == "Norway" & Territory == "Svalbard Isl. (Norway)" |
        Territory == "Sicily (Italy)" & Neighbour == "Sardinia (Italy)" |
        Neighbour == "Sicily (Italy)" & Territory == "Sardinia (Italy)" |
        Territory == "South Africa (Atlantic Coast)" & Neighbour == "South Africa (Indian Ocean Coast)" |
        Neighbour == "South Africa (Atlantic Coast)" & Territory == "South Africa (Indian Ocean Coast)" |
        Territory == "USA (Alaska, Arctic)" & Neighbour == "USA (Alaska, Subarctic)" |
        Neighbour == "USA (Alaska, Arctic)" & Territory == "USA (Alaska, Subarctic)"
    ) %>%
    group_by(Territory,Neighbour) %>% 
    summarise(n())

  # Cleaned results 
  Clean_Results_Trans <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("Territory","Neighbour")
    ) %>% 
    filter(Same_Nation == "No") %>% 
    select(-8,-9)

  # ---------------------------- #

  # Load and clean Discrete results
  Discrete_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")) %>% 
    left_join(Exploited_Species)

@@

### Non-transboundary

Discrete_Spp <- Clean_Results_Trans %>% 
  filter(
         Area_Index < Min_AI |
         Area_Index > Max_AI,
         Model_Index == MI#,
         # Same_Nation == "No"
         ) %>% 
  group_by(Territory) %>% 
  summarise(
    n_no_discrete_spp = length(unique(TaxonKey)),
    n_Territories = length(unique(Territory))
    )

@@

@@

Countries_Data <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI
         ) %>% 
  group_by(Territory = CT_fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey))) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(individual = fishing_entity,group) %>% 
  summarise(Total_trans = sum(value,na.rm=T)) %>% 
  filter(!is.na(individual)) %>% 
  select(individual,group,value=Total_trans) %>% 
  arrange(group,value)

Discrete_Data <- Countries_Data %>% 
  group_by(group) %>% 
  top_n(-3) %>% 
  mutate(value = value*-1)

Median_trans <- median(Countries_Data$value,na.rm=T)
Char <- as.factor(Countries_Data$group)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- length(unique(Countries_Data$group))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Countries_Data)) )
colnames(to_add) <- colnames(Countries_Data)
to_add$group <- rep(levels(Char), each=empty_bar)
Countries_Data <- bind_rows(Countries_Data, to_add)
Countries_Data <- Countries_Data %>% arrange(group,value)
Countries_Data$id <- seq(1, nrow(Countries_Data))

@@

# -------------------------- #
# Make the plot
# -------------------------- #

@@

  geom_bar(data = Discrete_Data,

@@

  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +

@@

  geom_segment(data=grid_data, aes(x = end, y = -20, xend = start, yend = -20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +

@@

  geom_segment(data=median_data, aes(x = end, y = median, xend = start+5, yend = median, colour = group),
               alpha=1, size=0.5 , inherit.aes = FALSE ) +

@@

@@

           x = rep(max(Countries_Data$id),7),
           y = c(-20,0,20, 40, 60, 80, 100),
           label = c("-20","0","20", "40", "60","80",">100"),
           color="grey", 
           size=3 , 
           angle=0, 

@@

@@

            aes(x=id, y=110,

@@

            alpha=0.6,

@@

  ylim(-140,140) + # sets the circle the first value the central the last value how wide

@@

    legend.position = c(0.5,0.5),

@@

#  Warring of missing values are the NA's for the columns

@@

ggsave(
    plot = last_plot(),
    width = 14,
    height = 10,
    units = "in",
    filename = "Territory_circular.tiff",
    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
  )

@@

```{r n_species_country, eval = T, echo =F}
# Number of countries shared by each Species
Species_Trans <- Clean_Results_Trans %>% 
  filter(
         Area_Index < Min_AI |
         Area_Index > Max_AI,
         Model_Index == MI
         ) %>% 
  group_by(TaxonKey) %>% 
  summarise(
    n_countries = length(unique(Territory))
  ) %>% 
  left_join(Exploited_Species) %>%
  left_join(Spp_Clasification)

@@

#### Overcounting transboundary stocks

@@

#### Fixing counts within EEZs

@@

#### Missing stocks

@@

@@

>>>>

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "wesanderson",
  "circlize", # For circular plot
  "ggimage", #for reading images to the circular plot
  # "cowplot",
  # "rgdal",
  # "RColorBrewer",
  # "knitr",
  # "kableExtra",
  "ggrepel", # for nice plot labels
  "ggsflabel", # for nice sf_plots labels
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "stringr",
  # "stringer",
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
  "parallel", # for parallelization
  "taxize", # For getting species names
  "rfishbase" # for species ecosystem affinity
)

@@

# Send second set of species

# Get species already modelled
# Removes everything before the number
Step_One <- gsub(".*_","",list.files(paste(Data_Path,"/Distribution_Data/SAU_Distribution/",sep="")))

exploited_species <- read.csv("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv") #%>% 
  # left_join(Spp_Clasification) %>% 
  # filter(!is.na(DemPel)) # remove freshwater spp

# Get all species in SAU database (2080)
Species_list <- exploited_species %>% 
  rename(scientific_name = TaxonName) %>% 
  pull(scientific_name)

# get their environ. association according to FishBase (species())

Species_environ_list <- rbind(species(Species_list, 
                                      fields = species_fields$habitat)
                              ) %>% 
  mutate(TaxonName = Species_list) %>% 
  left_join(exploited_species,  by ="TaxonName") %>% 
  filter(!TaxonKey %in% Species_List) %>% 
  filter(Saltwater == -1) %>%  # remove those that are not happy with saltwater
  select(TaxonKey,TaxonName,CommonName)

# write.csv(Species_environ_list,
#           "Transboundary_Spp_Set2.csv",
#           row.names = F)

# Sent to Gabs Seprember 16th

@@

@@

@@

#### For testing 
# Spp <- 600004  # Anchovie Equator, Chile and Peru
# Spp <- 600107 # Tuna Many RFMOs
# Spp <- 600464 # Discrete species 
# Spp <- 600051 # One of Pierrs massive (wrong) discrete spp
# x <- c(600464, # Discreat spp in one nation
      # 600059, # nowhere to be found spp
       # 601352, # Discrete spp in two nations
       # 600004) # transboundary spp
# Model <- "All"
# Coord <- CoorG
# 
# # For EEZ
Neighbours <- Neighbours_Data
Index_Code <- Index_Code
#  
# __________________________________
# __________________________________

# The function
EstTransIndex <- function(Spp,Model = "All",Neighbours,Coord,Index_Code,Save="Y",Jurisdiction_Type){

@@

  # Step 2.1. Determines discrete spp
  if(nrow(Spp_Grid) == 0 & Save == "Y"){

    #  Get the Territory where species happen
  Discrete_Territory <- unique(Model_Index_D$Territory)
  n_Territory <- length(Discrete_Territory)

@@

    # Set new data
    Current_Spp <- tibble(TaxonKey = as.integer(Spp),
                          Territory = Discrete_Territory)

@@

@@

  # Step 3. Sum total grids per Neighbours
  if(nrow(Spp_Grid) > 0 & Save == "Y"){

@@

  # Merge dataframes to get totals per Neighbourds
  Area_Index_D <- full_join(Territory_T,
                            Neighbour_T, 
                            by = c("Model_Index","Name","TaxonKey")
  ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(Territory = Name,
           Neighbour =Territory,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbour = n_spp_eez.y) %>% 
    mutate(Area_Index = n_spp_Country/Spp_Total) %>%  #Estimates the proportion of grids per country
    select(1:3,6,8)

  #____________ FINAL INDEX TABLE_________ #
  Indexes <- Model_Index_D %>% 
    full_join(Area_Index_D,
              by = c("TaxonKey","Territory","Model_Index")
    ) %>% 
    filter(!is.na(Area_Index),
           !is.na(Model_Index) # Uncomment after producing Models x datasets
    ) %>%  # Remove cases where the country does not pass the area_index and viceversa
    select(TaxonKey,Territory,Neighbour,everything())

@@

  } # Closes Treshold (Step 3)
} # closes function

@@

# Determine forlder for saving results
Folder <- "Trans_Results"
Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "")

if(file.exists(Results_Path) == TRUE){
  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "")
}else{
  dir.create(paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = ""))
  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "")
}

@@

# Load Jursidiction-dependant data

# Load neighbours data from previouse routine
Neighbours_Data <- fread(paste(Data_Path,"Spatial_Data/EEZ_Neighbours_List.csv", sep =""))

@@

@@

# Just a warning for me not to forget
print(paste("You are running the model for",nrow(Exploited_Species),"Species at the",Jurisdiction,"level and will be saved at",Folder))
```

@@

## Function `CleanResults`

```{r cleaning_function, eval = T, echo = F}

# Requires Clean_sau_eez_fes

CleanResults <- function(Data){

# Clean out countries that share with their own borders (e.g. USA gulf of Mx and East coast)
  Auto_Remove_Territories <- Data %>%   
    rename(FishingRegion=Territory) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(TaxonKey,
           Territory= FishingRegion,
           FishingRegion=Neighbour, 
           Model_Index,
           Area_Index,
           CT_fishing_entity= fishing_entity) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(1,2, 
           Neighbour = FishingRegion,
           Model_Index:CT_fishing_entity,
           NT_fishing_entity= fishing_entity,
           everything()) %>% 
    mutate(
      CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Territory),paste(CT_fishing_entity)),
      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour),paste(NT_fishing_entity)),
      Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
    )

  Territories_to_Remove <- Data %>% 
    filter(
      Territory %in% Islands_to_Remove |
        Neighbour %in% Islands_to_Remove |
        Territory == "Balearic Island (Spain)" & Neighbour == "Spain (Mediterranean and Gulf of Cadiz)" |
        Territory == "British Virgin Isl. (UK)" & Neighbour == "Anguilla" |
        Neighbour == "British Virgin Isl. (UK)" & Territory == "Anguilla" |
        Territory == "Corsica (France)" & Neighbour == "France (Mediterranean)" |
        Neighbour == "Corsica (France)" & Territory == "France (Mediterranean)" |
        Territory == "Crete (Greece)" & Neighbour == "Grece" |
        Neighbour == "Crete (Greece)" & Territory == "Grece" |
        Territory == "Cyprus (North)" & Neighbour == "Cyprus (South)" |
        Neighbour == "Cyprus (North)" & Territory == "Cyprus (South)" |
        Territory == "Channel Isl. (UK)" & Neighbour == "United Kingdom" |
        Neighbour == "Channel Isl. (UK)" & Territory == "United Kingdom" |
        Territory == "Glorieuse Islands (France)" & Neighbour == "Mayotte (France)" |
        Neighbour == "Glorieuse Islands (France)" & Territory == "Mayotte (France)" |
        Territory == "Guam (USA)" & Neighbour == "Northern Marianas (USA)" |
        Neighbour == "Guam (USA)" & Territory == "Northern Marianas (USA)" |
        Territory == "Italy" & Neighbour == "Sardinia (Italy)" |
        Neighbour == "Italy" & Territory == "Sardinia (Italy)" |
        Territory == "Italy" & Neighbour == "Sicily (Italy)" |
        Neighbour == "Italy" & Territory == "Sicily (Italy)" |
        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (main islands)"|
        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (main islands)"|
        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (Ogasawara Islands)"|
        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (Ogasawara Islands)"|
        Territory == "Norway" & Neighbour == "Svalbard Isl. (Norway)" |
        Neighbour == "Norway" & Territory == "Svalbard Isl. (Norway)" |
        Territory == "Sicily (Italy)" & Neighbour == "Sardinia (Italy)" |
        Neighbour == "Sicily (Italy)" & Territory == "Sardinia (Italy)" |
        Territory == "South Africa (Atlantic Coast)" & Neighbour == "South Africa (Indian Ocean Coast)" |
        Neighbour == "South Africa (Atlantic Coast)" & Territory == "South Africa (Indian Ocean Coast)" |
        Territory == "USA (Alaska, Arctic)" & Neighbour == "USA (Alaska, Subarctic)" |
        Neighbour == "USA (Alaska, Arctic)" & Territory == "USA (Alaska, Subarctic)"
    ) %>%
    group_by(Territory,Neighbour) %>% 
    summarise(n())

  # Cleaned results 
  Clean_Results <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("Territory","Neighbour")
    ) %>% 
    filter(Same_Nation == "No") %>% 
    select(-8,-9)

  return(Clean_Results)

# x <- Clean_Results(Discrete_Data)

@@

@@

  # List of species
  Spp <- list.files(paste(Results_Path,"/Trans_Results",sep=""))[-829]

  # Load and clean Transboundary results
  Results_Trans <- GetTransResults(Spp)

  # Clean results susing function CleanResultsfun
  Clean_Results_Trans <- CleanResults(Results_Trans)

  # Load and clean Discrete results
  Discrete_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")) %>% 
    filter(!is.na(TaxonKey)) %>% 
    select(2:3)

@@

### Non-transboundary
# 
# Partial_Transboundary_Spp <- Clean_Results_Trans %>% 
#   filter(
#          Area_Index >= Min_AI,
#          Area_Index <= Max_AI,
#          Model_Index == MI
#          ) 
# 
# Discrete_Spp_Area_Index <- Clean_Results_Trans %>% 
#   filter(
#     Area_Index >= Max_AI, # Discrete spp only on countryes with > 75%
#     # Area_Index <= Min_AI,
#          Model_Index == MI
#          ) %>% 
#   anti_join(Partial_Transboundary_Spp, # Removes species if it is already transboundary in a country
#             by = c("TaxonKey","Territory")
#   ) %>% 
#   group_by(Territory) %>% 
#   summarise(
#     n_discrete_spp = length(unique(TaxonKey))
    )

# Discrete_Spp <- Discrete_Data %>% 
#   group_by(Territory) %>% 
#   summarise(
#     n_discrete_spp = length(unique(TaxonKey))
#     ) %>% 
#   bind_rows(Discrete_Spp_Area_Index) %>% 
#   group_by(Territory) %>% 
#   summarise(n_discrete = sum(n_discrete_spp))

  # Merging eezs by territories (e.g. Mex Atlantic and pacific to Mez)
Country_Discrete_Data <- Discrete_Data %>% 
  rename(eez_name = Territory) %>% 
  left_join(sau_eez_fes) %>% 
  group_by(Territory = fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey)))

@@

```{r Circular_Data, eval = T, echo = F}

# -------------------------- #
# Transboundary data
# -------------------------- #

Countries_Data <- Clean_Results_Trans %>% 
  filter(
    Area_Index >= Min_AI,
    Area_Index <= Max_AI,
    Model_Index == MI
  ) %>% 
  group_by(Territory = CT_fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey))) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(individual = fishing_entity,group) %>% 
  summarise(Total_trans = sum(value,na.rm=T)) %>% 
  mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
  filter(!is.na(individual)) %>% 
  select(individual,group,value) %>% 
  arrange(group,value)

# -------------------------- #
# Discrete data
# -------------------------- #

Discrete_Data <- Clean_Results_Trans %>% 
  filter(Model_Index == MI) %>% 
  ## Determine as Trans. those species that are both trans and discrete for a nation (Tresh 2 and 3)
  mutate(Species_Type = ifelse(Area_Index > Max_AI,"Discrete",
                                ifelse(Area_Index < Min_AI,NA,
                                "Transboundary"))
         ) %>% 
  filter(!is.na(Species_Type)) %>% 
  group_by(CT_fishing_entity,Species_Type,TaxonKey) %>%
  summarise(n=n()) %>%
  spread(Species_Type,n) %>% 
  mutate(Discrete = ifelse(!is.na(Discrete) & !is.na(Transboundary),NA,Discrete)) %>% 
  gather("Species_Type","value", Discrete:Transboundary) %>% 
  filter(!is.na(value),
         Species_Type == "Discrete") %>% 
  group_by(Territory = CT_fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey)),
            Taxons = paste(unique(TaxonKey),collapse = ";")) %>% 
  #  Include discrete species of Trsh. 1
  bind_rows(Country_Discrete_Data) %>%
  # Data cleaning (group by territory and include georegions for plot)
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(Territory = fishing_entity) %>% 
  summarise(value =sum(value,na.rm = T)*-1) %>% # Multyply them by -1 so they appear negative on plot
  mutate(value = ifelse(value <= -100,-100,value)) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  filter(!is.na(Territory)) %>% 
  select(individual = Territory,
         group,
         value)

# Include possible missing countries in bothe datasets
Countries_Data <- Discrete_Data %>% 
  anti_join(Countries_Data,
            by = c("individual","group")) %>% 
  mutate(Total_Discrete = 0) %>% 
  bind_rows(Countries_Data)

Discrete_Data <- Countries_Data %>% 
  anti_join(Discrete_Data,
            by = c("individual","group")) %>% 
  mutate(value = 0) %>% 
  bind_rows(Discrete_Data)

@@

# -------------------------- #
# Data manipulation for plot
# -------------------------- #

# Set a number of 'empty bar' to add at the end of each group
Char <- as.factor(Countries_Data$group) # Set groups to factors
empty_bar <- length(unique(Countries_Data$group))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Countries_Data)) )
colnames(to_add) <- colnames(Countries_Data)
to_add$group <- rep(levels(Char), each=empty_bar)
Countries_Data <- bind_rows(Countries_Data, to_add)
Countries_Data <- Countries_Data %>% arrange(group,value)
Countries_Data$id <- seq(1, nrow(Countries_Data))

@@

# -------------------------- #
# Get id to Discrete data
# -------------------------- #

Discrete_Data_Plot <- Discrete_Data %>% 
  left_join(Countries_Data,
            by =c("individual","group")
  ) %>%
  mutate(value = ifelse(value.x <= -100,-100,value.x)) %>%
  select(individual,group,value,id) %>%
  arrange(group,value)

### make sure they have all same countries

Discrete_Data_Plot %>% 
  anti_join(Countries_Data,
            by = c("individual","group","id"))

# -------------------------- #
# Make the plot
# -------------------------- #

# Global Variables
Seq_axis <- seq(-100,100,20)
Plot_Limit <- max(Countries_Data$value,na.rm=T)
Plot_Limit_Low <- -110
Ticks_Color <- "grey50"

@@

  geom_bar(data = Discrete_Data_Plot,

@@

  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +

@@

  geom_segment(data=grid_data, aes(x = end, y = -100, xend = start, yend = -100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = -80, xend = start, yend = -80), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = -60, xend = start, yend = -60), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = -40, xend = start, yend = -40), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = -20, xend = start, yend = -20), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +

@@

  geom_segment(data=median_data,
               aes(x = end,
                   y = median,
                   xend = start+5, 
                   yend = median,
                   colour = group),
               alpha=1,
               size=0.5 , 
               inherit.aes = FALSE ) +

@@

  annotate("text", label = "Transboundary", x = 214, y = 45, size = 5, colour = "grey10", angle = 90) +
  annotate("text", label = "Discrete", x = 210, y = -45, size = 5, colour = "grey10", angle = 90) +

@@

           x = rep(max(Countries_Data$id),length(Seq_axis)),
           y = Seq_axis,
           label = c("<-100",as.character(Seq_axis)[2:(length(Seq_axis)-1)],">100"),
           color = Ticks_Color, 
           size= 4, 
           angle = 0, 

@@

  #Country labels

@@

            aes(x=id, y=Plot_Limit,

@@

            alpha=1,

@@

  ylim(Plot_Limit_Low,Plot_Limit) + # sets the circle the first value the central the last value how wide

@@

    # legend.position = c(0.5,0.5),
    legend.position = "",

@@

                      na.value = "white")

@@

ggsave(
    plot = last_plot(),
    width = 12,
    height = 12,
    units = "in",
    filename = "Territory_circular_both.png",
    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
  )

@@

```{r n_species_country, eval = T, echo =F}

# Number of countries shared by each Species
Species_Trans <- Clean_Results_Trans %>% 
  filter(
         Area_Index < Min_AI |
         Area_Index > Max_AI,
         Model_Index == MI
         ) %>% 
  group_by(TaxonKey) %>% 
  summarise(
    n_countries = length(unique(Territory))
  ) %>% 
  left_join(Exploited_Species) %>%
  left_join(Spp_Clasification)

@@

### Overcounting transboundary stocks

@@

### Fixing counts within EEZs

@@

### Missing stocks

@@

### Pierrs massive discrete stocks

```{r Pierrs_Discretion, eval = F ,echo = T,warning = F,message = F}

Pierre <-  Clean_Results_Trans %>% 
  filter(Territory == "Saint Pierre & Miquelon (France)") %>% 
  left_join(Exploited_Species,
            by = "TaxonKey")

# Very wrong!
# using 600051 to see what's the problem with the Area index

# Found the problem, Territory and Neighbour were switched un the last step of the EstTransSpp function

@@

```{r Continent_PNG, eval =F }

names(UN_Regions)
# Load Land shapefile
path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
# #The File
fnam_world_land <- "ne_50m_admin_0_countries.shp"

World_land_sf <- st_read(dsn = path_world_land,
                         layer =file_path_sans_ext(fnam_world_land)) %>% 
  st_transform(crs = 4326)

head(World_land_sf)
